\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-20 icse/compiler.tex
Typo fixes

\subsection{Tokenizer}
Before compiling abstract algorithms, {\sf Tokenizer} first tokenizes
each abstract algorithm into a list of tagged tokens.  An algorithm
consists of ordered steps and it may contain sub-steps as well.
For example, the \textbf{\small ToPrimitive} algorithm in
Figure~\ref{fig:to-primitive}(a) has three steps and the second step
has seven sub-steps.  Moreover, the tokens of each step have their own
HTML tags and each tag has a meaning.  For instance, \code{<var>}
denotes variables, \code{<emu-grammar>} denotes productions, and
\code{<code>} denotes ECMAScript code.
% \[
%   \begin{array}{c|l}
%     \text{HTML tags} & \text{meanings}\\\hline\hline
%     \code{<var>} & \text{variables}\\\hline
%     \code{<emu-grammar>} & \text{productions}\\\hline
%     \code{<emu-nt>} & \text{non-terminal syntax}\\\hline
%     \code{<code>} & \text{ECMAScript codes}\\\hline
%     \code{<emu-const>} & \text{constant values}\\\hline
%     \code{<emu-val>} & \text{values}\\\hline
%     \code{<ol>} & \text{ordered sub-steps}\\\hline
%     \code{<ul>} & \text{unordered sub-steps}\\\hline
%     \code{<sup>} & \text{superscripts}\\\hline
%     \text{otherwise} & \text{simple texts}\\\hline
%   \end{array}
% \]
We keep such HTML tag information for each token to generate more precise
{\sf Compile Rules}.  For example, because if and only if a token has
a tag \( \code{<var>} \), it is a parameter or a local variable, we can
construct {\sf Compile Rules} that precisely distinguish identifiers
from other components.

@@

\subsection{Token AST Converter}
Conversion rules describe how to generate an \( \ires \) function for a
given token AST.  Each conversion rule is defined with its
corresponding parsing rule.  For basic token parsers, their conversion
rules always return the string values of the contents in parsed tokens.
For example, the following conversion rules are the omitted parts
in the previous example for the step 2-e-i of \textbf{ToPrimitive}:
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = ... ^^ { case _ ~ x ~ _ ~ y => ILet(x, y) }
// expressions
val Expr =
  // identifiers   // return if abrupt
  ... ^^ EId |||   ... ^^ { _ ~ e => EAbrupt(e) } |||
  // function calls
  ... ^^ { case x ~ _ ~ y ~ _ => ECall(x, y) }    |||
  // lists
  ... ^^ { case _ ~ x ~ _ => EList(e) }
)
\end{lstlisting}
The conversion rule of the compile rule \( \code{Stmt} \) uses only
the second and fourth sub trees and converts them to \( \ires \)
components.  The second sub-tree is converted to a string value
because it was constructed via the basic token parser \( \code{varT} \).
The fourth sub-tree is converted to an \( \ires \) expression
because the conversion rules of the \( \code{Expr} \) compile rule
construct \( \ires \) expressions.  Then, the conversion rule of
\( \code{Stmt} \) constructs the lexical binding instruction \( \code{ILet} \)
with the string value and the \( \ires \) expression.  In this way,
the step 2-e-i of \textbf{ToPrimitive} is converted to the following
instruction:
\begin{lstlisting}[style=ires]
let result = ? (Call exoticToPrim input (new [hint]))
\end{lstlisting}

@@

\item \textbf{Abstract data types:} \( \ires \) supports only three
abstract data types: \( \code{Record} \) for mappings from some values
to other values, \( \code{List} \) for sequential data, and
\( \code{Singleton} \) for singleton data.  For example, ECMAScript
environment records are represented as \( \code{Record} \)
from string values into addresses that represents other type of
\( \code{Record} \) for bindings.  We also represent constants
in the ECMAScript specification such as \( \code{empty} \)
and \( \code{normal} \) as \( \code{Singleton} \) data types
in \( \ires \).
\end{itemize}

>>>>

\subsection{Tokenizer}
Before compiling abstract algorithms, {\sf Tokenizer} first tokenizes
each abstract algorithm into a list of tagged tokens.  An algorithm
consists of ordered steps, and a step may contain sub-steps as well.
For example, the \textbf{\small ToPrimitive} algorithm in
Figure~\ref{fig:to-primitive}(a) has three steps and the second step
has seven sub-steps.  Moreover, the tokens of each step have their own
HTML tags and each tag has a meaning.  For instance, \code{<var>}
denotes variables, \code{<emu-grammar>} denotes productions, and
\code{<code>} denotes ECMAScript code.
% \[
%   \begin{array}{c|l}
%     \text{HTML tags} & \text{meanings}\\\hline\hline
%     \code{<var>} & \text{variables}\\\hline
%     \code{<emu-grammar>} & \text{productions}\\\hline
%     \code{<emu-nt>} & \text{non-terminal syntax}\\\hline
%     \code{<code>} & \text{ECMAScript codes}\\\hline
%     \code{<emu-const>} & \text{constant values}\\\hline
%     \code{<emu-val>} & \text{values}\\\hline
%     \code{<ol>} & \text{ordered sub-steps}\\\hline
%     \code{<ul>} & \text{unordered sub-steps}\\\hline
%     \code{<sup>} & \text{superscripts}\\\hline
%     \text{otherwise} & \text{simple texts}\\\hline
%   \end{array}
% \]
We keep such HTML tag information for each token to generate more precise
{\sf Compile Rules}.  For example, because if and only if a token has
a tag \( \code{<var>} \), it is a parameter or a local variable, we can
construct {\sf Compile Rules} that precisely distinguish identifiers
from other components.

@@

\subsection{Token AST Converter}
Conversion rules describe how to generate an \( \ires \) function for a
given token AST.  Each conversion rule is defined with its
corresponding parsing rule.  For basic token parsers, their conversion
rules always return the string values of the contents in parsed tokens.
For example, the following conversion rules are the omitted parts
in the previous example for the step 2-e-i of \textbf{ToPrimitive}:
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = ... ^^ { case _ ~ x ~ _ ~ y => ILet(x, y) }
// expressions
val Expr =
  // identifiers   // return if abrupt
  ... ^^ EId |||   ... ^^ { _ ~ e => EAbrupt(e) } |||
  // function calls
  ... ^^ { case x ~ _ ~ y ~ _ => ECall(x, y) }    |||
  // lists
  ... ^^ { case _ ~ x ~ _ => EList(e) }
)
\end{lstlisting}
The conversion rule of the compile rule \( \code{Stmt} \) uses only
the second and fourth sub trees and converts them to \( \ires \)
instructions.  The second sub-tree is converted to a string value
because it was constructed via the basic token parser \( \code{varT} \).
The fourth sub-tree is converted to an \( \ires \) expression
because the conversion rules of the \( \code{Expr} \) compile rule
construct \( \ires \) expressions.  Then, the conversion rule of
\( \code{Stmt} \) constructs the lexical binding instruction \( \code{ILet} \)
with the string value and the \( \ires \) expression.  In this way,
the step 2-e-i of \textbf{ToPrimitive} is converted to the following
\( \ires \) instruction:
\begin{lstlisting}[style=ires]
let result = ? (Call exoticToPrim input (new [hint]))
\end{lstlisting}

@@

\item \textbf{Abstract data types:} \( \ires \) supports only three
abstract data types: \( \code{Record} \) for mappings from some values
to other values, \( \code{List} \) for sequential data, and
\( \code{Singleton} \) for singleton data.  For example, ECMAScript
environment records are represented as \( \code{Record} \)
from string values into addresses that represent other types of
\( \code{Record} \) for bindings.  We also represent constants
in the ECMAScript specification such as \( \code{empty} \)
and \( \code{normal} \) as \( \code{Singleton} \) data types
in \( \ires \).
\end{itemize}
